The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors. However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” (Freytag Andreas, Thurik Roy, 2007). Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.

>>>>

What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors. However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” [(Freytag Andreas, Thurik Roy, 2007)](Freytag2007). Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
